12 strains

### 2021-11-13 experiments/12_strains/12_strains.Rmd
reorganisation, and added different number of strains

---
title: "experiment 1"
author: "Owen Petchey"
date: "6/25/2021"
output:
  pdf_document: default
  html_document:
    keep_md: yes
---

@@

library(microxanox)
if (packageVersion("microxanox") < package_version("0.3.0")) {
  stop("microxanox version needs to be at least 0.3.0!")
}
library(tidyverse)
library(patchwork)
library(here)
source(here("R/various_useful_functions.r"))
zero <- 0 ## don't change
unity <- 1 ## don't change!!!
options(mc.cores = 7)
eval_dynamics_flag <- FALSE
```

@@

num_CB_strains <- 9
num_SB_strains <- 9
num_PB_strains <- 9

@@

parameter <- new_runsim_parameter(
  dynamic_model = bushplus_dynamic_model,
  event_definition = event_definition_1,
  event_interval = 100,
  noise_sigma = 0,
  minimum_abundances = rep(1, 3),
  sim_duration = 2000,
  sim_sample_interval = 100,
  strain_parameter = sp,
  log10a_series = c(
    log10(sp$a_O),
    log10(sp$a_O)
  )
)
names(parameter$minimum_abundances) <- c("CB", "PB", "SB")
rm(sp)

@@

```{r eval = eval_dynamics_flag}
parameter$log10a_series <- c(-1, -7, -7)
parameter$strain_parameter <- var_expt$pars[[no_diversity]]
parameter$strain_parameter$initial_state <- new_initial_state(
  num_CB_strains,
  num_PB_strains,
  num_SB_strains,
  values = "bush_ssfig3"
)
parameter$strain_parameter$initial_state[grep("CB_", names(parameter$strain_parameter$initial_state))] <- 10^10/num_CB_strains
sim_res_novar1 <- run_simulation(parameter)
saveRDS(sim_res_novar1, here("experiments/experiment 1/data/sim_res_novar1.RDS"))
```

```{r}
sim_res_novar1 <- readRDS(here("experiments/experiment 1/data/sim_res_novar1.RDS"))
plot_dynamics(sim_res_novar1)
#ggsave(here("simulations/expt2/figures/switching_novar.pdf"), width = 10)
```

@@

```{r eval = eval_dynamics_flag}
parameter$strain_parameter <- var_expt$pars[[medium_diverity_varexp_row]]
parameter$strain_parameter$initial_state <- sim_res_novar1$strain_parameter$initial_state
sim_res_highvar1 <- run_simulation(parameter)
saveRDS(sim_res_highvar1, here("experiments/experiment 1/data/sim_res_highvar1.RDS"))
```

```{r}
sim_res_highvar1 <- readRDS(here("experiments/experiment 1/data/sim_res_highvar1.RDS"))
plot_dynamics(sim_res_highvar1)
#ggsave(here("simulationsexpt2/figures/switching_highvar.pdf"), width = 10)

@@

```{r eval = eval_dynamics_flag}
parameter$log10a_series <- c(-5, -3, -1, -1)
parameter$strain_parameter <- var_expt$pars[[no_diversity]]
parameter$strain_parameter$initial_state <- new_initial_state(
  num_CB_strains,
  num_PB_strains,
  num_SB_strains,
  values = "bush_ssfig3"
)
parameter$strain_parameter$initial_state[grep("CB_", names(parameter$strain_parameter$initial_state))] <- 10/num_CB_strains
sim_res_novar2 <- run_simulation(parameter)
saveRDS(sim_res_novar2, here("experiments/experiment 1/data/sim_res_novar2.RDS"))
```

```{r}
sim_res_novar2 <- readRDS(here("experiments/experiment 1/data/sim_res_novar2.RDS"))
plot_dynamics(sim_res_novar2)
#ggsave(here("simulations/expt2/figures/switching_novar.pdf"), width = 10)
```

@@

```{r eval = eval_dynamics_flag}
parameter$strain_parameter <- var_expt$pars[[medium_diverity_varexp_row]]
parameter$strain_parameter$initial_state <- sim_res_novar2$strain_parameter$initial_state
sim_res_highvar2 <- run_simulation(parameter)
saveRDS(sim_res_highvar2, here("experiments/experiment 1/data/sim_res_highvar2.RDS"))
```

```{r}
sim_res_highvar2 <- readRDS(here("experiments/experiment 1/data/sim_res_highvar2.RDS"))
plot_dynamics(sim_res_highvar2)
#ggsave(here("simulationsexpt2/figures/switching_highvar.pdf"), width = 10)

@@

```{r eval = eval_dynamics_flag}
parameter$log10a_series <- c(-1, -8, -1)
parameter$strain_parameter <- var_expt$pars[[no_diversity]]
parameter$strain_parameter$initial_state <- new_initial_state(
  num_CB_strains,
  num_PB_strains,
  num_SB_strains,
  values = "bush_ssfig3"
)
parameter$strain_parameter$initial_state[grep("CB_", names(parameter$strain_parameter$initial_state))] <- 10/num_CB_strains
sim_res_novar3 <- run_simulation(parameter)
saveRDS(sim_res_novar3, here("experiments/experiment 1/data/sim_res_novar3.RDS"))
```

```{r}
sim_res_novar3 <- readRDS(here("experiments/experiment 1/data/sim_res_novar3.RDS"))
plot_dynamics(sim_res_novar3)
#ggsave(here("simulations/expt2/figures/switching_novar.pdf"), width = 10)
```

@@

```{r eval = eval_dynamics_flag}
parameter$strain_parameter <- var_expt$pars[[medium_diverity_varexp_row]]
parameter$strain_parameter$initial_state <- sim_res_novar3$strain_parameter$initial_state
sim_res_highvar3 <- run_simulation(parameter)
saveRDS(sim_res_highvar3, here("experiments/experiment 1/data/sim_res_highvar3.RDS"))
```

```{r}
sim_res_highvar3 <- readRDS(here("experiments/experiment 1/data/sim_res_highvar3.RDS"))
plot_dynamics(sim_res_highvar3)
#ggsave(here("simulationsexpt2/figures/switching_highvar.pdf"), width = 10)

@@

saveRDS(parameter, here("experiments/experiment 1/data/parameter_1e6_x2x6_factorial.RDS"))
saveRDS(var_expt_small, here("experiments/experiment 1/data/var_expt_1e6_x2x6_factorial.RDS"))
```

### for testing

```{r eval = FALSE}
var_expt_small <- var_expt[c(no_diversity, medium_diverity_varexp_row),]
saveRDS(parameter, here("experiments/experiment 1/data/parameter_1e6_x2x6_factorial.RDS"))
saveRDS(var_expt_small, here("experiments/experiment 1/data/var_expt_1e6_x2x6_factorial_small.RDS"))
run_ss_var_experiment(
  parameter = readRDS(here("experiments/experiment 1/data/parameter_1e6_x2x6_factorial.RDS")), 
  var_expt = readRDS(here("experiments/experiment 1/data/var_expt_1e6_x2x6_factorial_small.RDS"))) %>%
saveRDS(here("experiments/experiment 1/data/ss_data_1e6_x2x6_factorial_small.RDS"))
```

@@

```{r run_experiment, eval = eval_dynamics_flag}
run_ss_var_experiment(
  parameter = readRDS(here("experiments/experiment 1/data/parameter_1e6_x2x6_factorial.RDS")), 
  var_expt = readRDS(here("experiments/experiment 1/data/var_expt_1e6_x2x6_factorial.RDS"))) %>%
saveRDS(here("experiments/experiment 1/data/ss_data_1e6_x2x6_factorial.RDS"))
```

@@

## sim length 1'000'000, 20 SBPBgrad, 2xCB variation, 6xSBPB variation
readRDS(here("experiments/experiment 1/data/ss_data_1e6_x2x6_factorial_small.RDS")) %>%
  mutate(sim_length = 1000000) %>% 
  multidplyr::partition(cluster) %>%
  mutate(stability_measures = list(get_stability_measures(ss_res))) %>%
  collect() %>%
  unnest(cols = c(stability_measures)) %>%
  saveRDS(here("experiments/experiment 1/data/stab_data_1e6_x2x6_factorial_small.RDS"))
```

```{r eval = FALSE}
## compare version 1 results to the current.
v1_ss_data <- readRDS(here("experiments/experiment 1/data/version1_ss_data_1e6_x2x6_factorial.RDS"))
v1_stab_data <- readRDS(here("experiments/experiment 1/data/version1_stab_data_1e6_x2x6_factorial.RDS"))

small_ss_data <- readRDS(here("experiments/experiment 1/data/ss_data_1e6_x2x6_factorial_small.RDS"))
small_stab_data <- readRDS(here("experiments/experiment 1/data/stab_data_1e6_x2x6_factorial_small.RDS"))

xxxxx <- small_stab_data %>%
  select(-data, -pars, -ss_by_a_N_result, -ss_res, -sim_length) %>%
  filter(Species == "O")
v1_stab_data %>%
  filter(CB_var_gmax_s == 0, CB_var_h_s == 0,
         SB_var_gmax_s == 0, SB_var_h_s == 0,
         PB_var_gmax_s == 0, PB_var_h_s == 0) %>%
  filter(Species == "O")
v1_stab_data %>%
  slice(9620) %>%
  filter(Species == "O")
```

```{r}
## find various combinations of diversity
var_expt <- readRDS(here("experiments/experiment 1/data/ss_data_1e6_x2x6_factorial.RDS"))
stab_data <- readRDS(here("experiments/experiment 1/data/stab_data_1e6_x2x6_factorial.RDS"))

@@

@@

#junk1 <- var_expt[no_diversity,]$ss_res[[1]]
```

@@

@@

```{r}
p_overlay1 <- plot_ss_result2(var_expt[no_diversity,]$ss_res[[1]],
                             var_expt[max_diversty_all,]$ss_res[[1]],
                             xlims = c(-7, -1))
p_overlay1
```

```{r}
p_overlay2 <- plot_ss_result2(var_expt[no_diversity,]$ss_res[[1]],
                             var_expt[max_only_CB_diversity,]$ss_res[[1]],
                             xlims = c(-7, -1))
p_overlay2

#ss_result1 <- var_expt[no_diversity,]$ss_res[[1]]
#ss_result2 <- var_expt[max_only_CB_diversity,]$ss_res[[1]]

```{r}
p_overlay3 <- plot_ss_result2(var_expt[no_diversity,]$ss_res[[1]],
                             var_expt[max_only_SBPB_diversity,]$ss_res[[1]],
                             xlims = c(-7, -1))
p_overlay3

#ss_result3 <- var_expt[max_only_SBPB_diversity,]$ss_res[[1]]

```{r}
tempp1 <- var_expt[no_diversity,]$ss_res[[1]] %>%
  filter(initial_N_CB == 1e10,
         log10(a_O) > -4.5, log10(a_O) < -4)
tempp2 <- var_expt[max_only_SBPB_diversity,]$ss_res[[1]] %>%
  filter(initial_N_CB == 1e10,
         log10(a_O) > -4.5, log10(a_O) < -4)

@@

```{r}
CB_vars <- unique(stab_data$CB_var_gmax_s)
SB_vars <- unique(stab_data$SB_var_gmax_s)

@@

### Raw
```{r}
all_stab_results %>%
  filter(Species == "O") %>%
  ggplot(aes(x = var_gmax, y = hyst_range_raw, col=var_treat, shape = as_factor(sim_length))) +
  geom_point() +
  xlab("Amount of trait variation\n[see text for units]") +
  ylab("Extent of bistability region\n[log10 oxygen diffusivity]") +
  labs(col = "Variation in\nonly these\nfunctional groups")
##ggsave("manuscript/figures/extent_of_bistab1.pdf", height = 4)

@@

```{r}
all_stab_results %>%
  filter(Species == "O") %>%
  ggplot(aes(x = var_gmax, y = hyst_range_log, col=var_treat, shape = as_factor(sim_length))) +
  geom_point() +
  xlab("Amount of trait variation\n[see text for units]") +
  ylab("Extent of bistability region\n[log10 oxygen diffusivity]") +
  labs(col = "Variation in\nonly these\nfunctional groups")
##ggsave("manuscript/figures/extent_of_bistab1.pdf", height = 4)

@@

# FROM HERE NOT CHANGED TO NEW FORMAT!!!!!!
# Some puzzles

## What effect of changing the length of the simulations
No Experimental data.

```{r, eval = FALSE, echo = FALSE}
var_expt1 <- readRDS(here("experiments/experiment 1/data/ss_data_1000000_20factorial.RDS"))
var_expt2 <- readRDS(here("experiments/experiment 1/data/ss_data_80000.RDS"))

p1_short  <- plot_ss_result1(var_expt2,
                result_index = max_diversty_all,
                filename_prefix = NULL,
                save_image_file = FALSE)
p1_short

p1_long  <- plot_ss_result1(var_expt1,
                result_index = max_diversty_all,
                filename_prefix = NULL,
                save_image_file = FALSE)
p1_long
```

## Puzzle 1

When the environment ameliorates for the sulphur bacteria, there is no strain replacement (in final state) along the oxygen diffusivity gradient -- either the system is oxic or the least tolerant strain SB9 dominates. And yet the switch to anoxic occurs earlier than when there is no diversity, which suggests there is some role of the more tolerant strains. Indeed Uriah showed that the presence of only the most tolerant strain is sufficient to give an earlier switch, even though it is not present in the final state when less tolerant strains are present. And he showed that the presence of only the least tolerant strain creates a later switch than when there are more tolerant strains.

The explanation is that the most tolerant strain does play a role, but only a transient one. The following dynamics are for the system starting oxic, and with a value of oxygen diffusivity (log10(a_O) = -4.8) for which the system remains oxic if there is no diversity, but switches to anoxic if there is diversity. There is only diversity in the sulphur bacteria. The most tolerant strain does at first grow, but is then outcompeted by less tolerant strains as the environment ameliorates (temporally).

TODO CHECK THE PARAMETER

```{r}
var_expt <- readRDS(here("experiments/experiment 1/data/ss_data_1e6_x2x6_factorial.RDS"))
var_expt_levels <- var_expt[,1:6]
no_diversity <- which(rowSums(abs(var_expt_levels))==0)
max_diversty_all <- which(max(rowSums(abs(var_expt_levels))) ==
                            rowSums(abs(var_expt_levels)))
max_only_CB_diversity <- which(max(rowSums(abs(var_expt_levels[,1:2]))) ==
                            rowSums(abs(var_expt_levels[,1:2])) &
                              rowSums(abs(var_expt_levels[,3:6]))==0)
max_only_SBPB_diversity <- which(max(rowSums(abs(var_expt_levels[,3:6]))) ==
                            rowSums(abs(var_expt_levels[,3:6])) &
                              rowSums(abs(var_expt_levels[,1:2]))==0)
```

```{r eval = eval_dynamics_flag}
parameter <- readRDS(here("experiments/experiment 1/data/sim_res_novar3.RDS"))
parameter$sim_duration <- 100000
parameter$result <- NULL
```

```{r eval = eval_dynamics_flag}
parameter$log10a_series <- c(-4.8, -4.8)
parameter$strain_parameter$initial_state <- new_initial_state(
  nrow(parameter$strain_parameter$CB),
  nrow(parameter$strain_parameter$PB),
  nrow(parameter$strain_parameter$PB),
  values = "bush_ssfig3"
)
parameter$strain_parameter$initial_state[grep("CB_", names(parameter$strain_parameter$initial_state))] <- 10^10/nrow(parameter$strain_parameter$CB)

sim_res_novar1 <- run_simulation(parameter)
saveRDS(sim_res_novar1, here("experiments/experiment 1/data/puzzle1_1.RDS"))
```

```{r, eval = FALSE, echo = FALSE}
sim_res_novar1 <- readRDS(here("experiments/experiment 1/data/puzzle1_1.RDS"))
plot_dynamics(sim_res_novar1)
#ggsave(here("simulations/expt2/figures/switching_novar.pdf"), width = 10)
```

```{r eval = FALSE, echo = FALSE}
sim_res_novar1 <- run_simulation(parameter_values = var_expt$pars[[max_only_SBPB_diversity]],
                          initial_state = initial_state)
saveRDS(sim_res_novar1, here("experiments/experiment 1/data/puzzle1_2.RDS"))
```

```{r, eval = FALSE, echo = FALSE}
sim_res_novar1 <- readRDS(here("experiments/experiment 1/data/puzzle1_2.RDS"))
plot_dynamics(sim_res_novar1)
#ggsave(here("simulations/expt2/figures/switching_novar.pdf"), width = 10)
```

## Zoom in on SS

```{r eval = FALSE, echo = FALSE}
a_Os <- 10^seq(-2.479, -2.4785, length=grid_num_a) ## sequence of a_0 values
initial_CBs <- 1#10^seq(0, 0, length=grid_num_N) ## sequence of N values
initial_PBs <- 1e8 ## not varied
initial_SBs <- 1e8 ## not varied
# next line creates all possible combinations
ss_expt <- expand.grid(N_CB = initial_CBs,
                      N_PB = initial_PBs,
                      N_SB = initial_SBs,
                      a_O = a_Os)
var_expt_master <- var_expt
var_expt <- var_expt_master[381,]
```

```{r, eval = FALSE, echo = FALSE}
#var_expt <- run_ss_var_experiment()
#saveRDS(var_expt, here("experiments/experiment 1/data/ss_data_zoom.RDS"))
```

```{r, eval = FALSE, echo = FALSE}
library(here)
zoom <- readRDS(here("experiments/experiment 1/data/ss_data_zoom.RDS"))

p1  <- plot_ss_result1(zoom,
                result_index = 1,
                filename_prefix = NULL,
                save_image_file = FALSE)
p1
```

## Negative abundance investigation

I (Owen) found that the sampling interval had an effect on the stability of the simulation. If the sampling interval was long, then in some rare cases (see below) the odesolver failed, with negative abundances occuring. I think this is due to abundances becoming very small, and then the computer having trouble with precision. I guess that when a sample is taken, the abundance is somehow altered if it is very low, probably by some rounding.

```{r eval = FALSE, echo = FALSE}
var_expt$pars[[1]]
dd <- var_expt$ss_res[[1]]
dd1 <- filter(dd, PB_1<(-0.0001))
dd1$a_O

ss_expt_master <- ss_expt
ss_expt <- ss_expt_master[abs(ss_expt_master$a_O - 1.336984e-05)<1e-10,]

var_expt_master <- var_expt
#var_expt <- var_expt[1,]
var_expt_test <- run_ss_var_experiment()
res <- var_expt_test$ss_res[[1]]

test1 <- ss_by_a_N(ss_expt, var_expt$pars[[1]])
x <- ss_expt[2,]
param <- var_expt$pars[[1]]
get_final_states_a_N(x, param)
ssfind_parameters <- param
ssfind_simulation_sampling_interval <- 1000
## now run inside the function "get_final_states_a_N"
simres1 <- simres
ssfind_simulation_sampling_interval <- 5000
## now run inside the function "get_final_states_a_N"
simres2 <- simres  # this fails

## now run inside the function "get_final_states_a_N"
plot_dynamics(simres2)

ggplot() +
  geom_line(data = simres1$result,
             mapping = aes(x = time, y = log10(PB_1))) +
  geom_point(data = simres2$result,
             mapping = aes(x = time, y = log10(PB_1))) +
  xlim(c(0, 250000))

ccc <- simres2$result

simres2$result$PB_1
simres2$result$time

log10_a <- log10(ss_expt$a_O[1]) ## very slowly goes anoxic
#log10_a <- log10(a_Os[354]) ## very slowly goes anoxic
#log10_a <- log10(a_Os[356]) ## very very very  slowly goes anoxic
#log10_a <- log10(a_Os[357]) ## does not go anoxic

default_dynamic_model <- bushplus_dynamic_model
default_event_definition <- event_definition_1
default_event_interval <- ssfind_simulation_duration
default_noise_sigma <- 0
default_minimum_abundances <- ssfind_minimum_abundances
default_sim_duration <- ssfind_simulation_duration
default_sim_sample_interval <- ssfind_simulation_duration
#initial_pars_from <- "bush_ssfig3"

default_log10a_series <- c(log10_a, log10_a)
initial_state <- new_initial_state(num_CB_strains,
                                   num_PB_strains,
                                   num_SB_strains,
                                   values = "bush_ssfig3")
initial_state[grep("CB_", names(initial_state))] <- 10^10/num_CB_strains
sim_res_novar <- run_simulation(parameter_values = var_expt$pars[[1]],
                          initial_state = initial_state)
plot_dynamics(sim_res_novar)

simulation_result <- sim_res_novar
every_n <- 1

chk <- sim_res_novar$result

sim_res_novar$result %>%
  ggplot() +
  geom_line(mapping = aes(x = time, y = PB_1))

#ggsave(here("simulations/expt2/figures/switching_novar.pdf"), width = 10)

## Understand about relative and absolute variation in traits

```{r echo = FALSE, eval = FALSE}
num_CB_strains <- 9
num_SB_strains <- 9
num_PB_strains <- 9

## multiplier of SBPB variation
CB_var_multiplier <- 1
SBPB_var_multiplier <- 5

num_div_treatment_levels <- 2

var_expt <- create_diversity_factorial(zero = zero, unity = unity, num_div_treatment_levels = num_div_treatment_levels)

display_diversity(
 4,
  var_expt = var_expt,
  num_CB_strains = num_CB_strains,
  num_SB_strains = num_SB_strains,
  num_PB_strains = num_PB_strains
)

this_one <- 4
CBtraits <- var_expt$pars[[this_one]]$CB
P <- 1 #10^seq(-5, 5, 0.1)
SR <- 10^seq(0, 3, 0.1)
gr_rateCB1 <- growth1(P, CBtraits$g_max_CB[1], CBtraits$k_CB_P[1]) * inhibition(SR, CBtraits$h_SR_CB[1])
gr_rateCB9 <- growth1(P, CBtraits$g_max_CB[num_CB_strains], CBtraits$k_CB_P[num_CB_strains]) * inhibition(SR, CBtraits$h_SR_CB[num_CB_strains])
CB_gr_rates <- (c(gr_rateCB1, gr_rateCB9))
CB_gr_range <- max(CB_gr_rates) - min(CB_gr_rates)
CB_gr_range

SBtraits <- var_expt$pars[[this_one]]$SB
P <- 1 #10^seq(-5, 5, 0.1)
SO <- 1
O <- 10^seq(-2.5, 2.5, 0.1)
gr_rateSB1 <- growth2(P, SO, SBtraits$g_max_SB[1], SBtraits$k_SB_P[1], SBtraits$k_SB_SO[1]) *
  inhibition(O, SBtraits$h_O_SB[1])
gr_rateSB9 <- growth2(P, SO, SBtraits$g_max_SB[9], SBtraits$k_SB_P[9], SBtraits$k_SB_SO[9]) *
    inhibition(O, SBtraits$h_O_SB[9])
SB_gr_rates <- (c(gr_rateSB1, gr_rateSB9))
SB_gr_range <- max(SB_gr_rates) - min(SB_gr_rates)
SB_gr_range

PBtraits <- var_expt$pars[[this_one]]$PB
P <- 1 #10^seq(-5, 5, 0.1)
SO <- 1
O <- 10^seq(-2.5, 2.5, 0.1)
gr_ratePB1 <- growth2(P, SO, PBtraits$g_max_PB[1], PBtraits$k_PB_P[1], PBtraits$k_PB_SR[1]) *
  inhibition(O, PBtraits$h_O_PB[1])
gr_ratePB9 <- growth2(P, SO, PBtraits$g_max_PB[9], PBtraits$k_PB_P[9], PBtraits$k_PB_SR[9]) *
  inhibition(O, PBtraits$h_O_PB[9])
PB_gr_rates <- (c(gr_ratePB1, gr_ratePB9))
PB_gr_range <- max(PB_gr_rates) - min(PB_gr_rates)
PB_gr_range

<!-- With the CB diversity multiplier set at ` CB_var_multiplier` and the SB/PB multiplier set at ` SBPB_var_multiplier` the range of realised growth rates of CB is ` CB_gr_range`, range of SB is ` SB_gr_range`, and range of PB is ` PB_gr_range`. -->

>>>>

---
title: "12 strains"
author: "Owen Petchey"
date: "6/25/2021"
output:
  pdf_document: default
  html_document:
    keep_md: yes
---

@@

library(microxanox)
if (packageVersion("microxanox") < package_version("0.3.0")) {
  stop("microxanox version needs to be at least 0.3.0!")
}
library(tidyverse)
library(patchwork)
library(here)
source(here("R/various_useful_functions.r"))
zero <- 0 ## don't change
unity <- 1 ## don't change!!!
options(mc.cores = 7)
eval_dynamics_flag <- FALSE
plot_ss_results <- FALSE
```

@@

num_CB_strains <- 12
num_SB_strains <- 12
num_PB_strains <- 12

@@

parameter <- new_runsim_parameter(
  solver_method = "radau",
  dynamic_model = bushplus_dynamic_model,
  event_definition = event_definition_1,
  event_interval = 10,
  noise_sigma = 0,
  minimum_abundances = rep(1, 3),
  sim_duration = 2000,
  sim_sample_interval = 100,
  strain_parameter = sp,
  log10a_series = c(
    log10(sp$a_O),
    log10(sp$a_O)
  )
)
names(parameter$minimum_abundances) <- c("CB", "PB", "SB")
rm(sp)

@@

```{r eval = eval_dynamics_flag}
parameter$log10a_series <- c(-1, -7, -7)
parameter$strain_parameter <- var_expt$pars[[no_diversity]]
parameter$strain_parameter$initial_state <- new_initial_state(
  num_CB_strains,
  num_PB_strains,
  num_SB_strains,
  values = "bush_ssfig3"
)
parameter$strain_parameter$initial_state[grep("CB_", names(parameter$strain_parameter$initial_state))] <- 10^10/num_CB_strains
parameter$solver_method <- "lsoda"
sim_res_novar1 <- run_simulation(parameter)
saveRDS(sim_res_novar1, here("experiments/12_strains/data/sim_res_novar1.RDS"))
```

```{r}
sim_res_novar1 <- readRDS(here("experiments/12_strains/data/sim_res_novar1.RDS"))
plot_dynamics(sim_res_novar1)
#ggsave(here("simulations/expt2/figures/switching_novar.pdf"), width = 10)
```

```{r}
simulation_result <- sim_res_novar1

@@

```{r eval = eval_dynamics_flag}
parameter$strain_parameter <- var_expt$pars[[medium_diverity_varexp_row]]
parameter$strain_parameter$initial_state <- sim_res_novar1$strain_parameter$initial_state
sim_res_highvar1 <- run_simulation(parameter)
saveRDS(sim_res_highvar1, here("experiments/12_strains/data/sim_res_highvar1.RDS"))
```

```{r}
sim_res_highvar1 <- readRDS(here("experiments/12_strains/data/sim_res_highvar1.RDS"))
plot_dynamics(sim_res_highvar1)
#ggsave(here("simulationsexpt2/figures/switching_highvar.pdf"), width = 10)

@@

```{r eval = eval_dynamics_flag}
parameter$log10a_series <- c(-5, -3, -1, -1)
parameter$strain_parameter <- var_expt$pars[[no_diversity]]
parameter$strain_parameter$initial_state <- new_initial_state(
  num_CB_strains,
  num_PB_strains,
  num_SB_strains,
  values = "bush_ssfig3"
)
parameter$strain_parameter$initial_state[grep("CB_", names(parameter$strain_parameter$initial_state))] <- 10/num_CB_strains
sim_res_novar2 <- run_simulation(parameter)
saveRDS(sim_res_novar2, here("experiments/12_strains/data/sim_res_novar2.RDS"))
```

```{r}
sim_res_novar2 <- readRDS(here("experiments/12_strains/data/sim_res_novar2.RDS"))
plot_dynamics(sim_res_novar2)
#ggsave(here("simulations/expt2/figures/switching_novar.pdf"), width = 10)
```

@@

```{r eval = eval_dynamics_flag}
parameter$strain_parameter <- var_expt$pars[[medium_diverity_varexp_row]]
parameter$strain_parameter$initial_state <- sim_res_novar2$strain_parameter$initial_state
sim_res_highvar2 <- run_simulation(parameter)
saveRDS(sim_res_highvar2, here("experiments/12_strains/data/sim_res_highvar2.RDS"))
```

```{r}
sim_res_highvar2 <- readRDS(here("experiments/12_strains/data/sim_res_highvar2.RDS"))
plot_dynamics(sim_res_highvar2)
#ggsave(here("simulationsexpt2/figures/switching_highvar.pdf"), width = 10)

@@

```{r eval = eval_dynamics_flag}
parameter$log10a_series <- c(-1, -8, -1)
parameter$strain_parameter <- var_expt$pars[[no_diversity]]
parameter$strain_parameter$initial_state <- new_initial_state(
  num_CB_strains,
  num_PB_strains,
  num_SB_strains,
  values = "bush_ssfig3"
)
parameter$strain_parameter$initial_state[grep("CB_", names(parameter$strain_parameter$initial_state))] <- 10/num_CB_strains
sim_res_novar3 <- run_simulation(parameter)
saveRDS(sim_res_novar3, here("experiments/12_strains/data/sim_res_novar3.RDS"))
```

```{r}
sim_res_novar3 <- readRDS(here("experiments/12_strains/data/sim_res_novar3.RDS"))
plot_dynamics(sim_res_novar3)
#ggsave(here("simulations/expt2/figures/switching_novar.pdf"), width = 10)
```

@@

```{r eval = eval_dynamics_flag}
parameter$strain_parameter <- var_expt$pars[[medium_diverity_varexp_row]]
parameter$strain_parameter$initial_state <- sim_res_novar3$strain_parameter$initial_state
sim_res_highvar3 <- run_simulation(parameter)
saveRDS(sim_res_highvar3, here("experiments/12_strains/data/sim_res_highvar3.RDS"))
```

```{r}
sim_res_highvar3 <- readRDS(here("experiments/12_strains/data/sim_res_highvar3.RDS"))
plot_dynamics(sim_res_highvar3)
#ggsave(here("simulationsexpt2/figures/switching_highvar.pdf"), width = 10)

@@

saveRDS(parameter, here("experiments/12_strains/data/parameter_1e6_x2x6_factorial.RDS"))
saveRDS(var_expt, here("experiments/12_strains/data/var_expt_1e6_x2x6_factorial.RDS"))
```

@@

```{r run_experiment, eval = eval_dynamics_flag}
run_ss_var_experiment(
  parameter = readRDS(here("experiments/12_strains/data/parameter_1e6_x2x6_factorial.RDS")), 
  var_expt = readRDS(here("experiments/12_strains/data/var_expt_1e6_x2x6_factorial.RDS"))) %>%
saveRDS(here("experiments/12_strains/data/ss_data_1e6_x2x6_factorial.RDS"))
```

@@

## sim length 1'000'000, 20 SBPBgrad, 2xCB variation, 6xSBPB variation
readRDS(here("experiments/12_strains/data/ss_data_1e6_x2x6_factorial_small.RDS")) %>%
  mutate(sim_length = 1000000) %>% 
  multidplyr::partition(cluster) %>%
  mutate(stability_measures = list(get_stability_measures(ss_res))) %>%
  collect() %>%
  unnest(cols = c(stability_measures)) %>%
  saveRDS(here("experiments/12_strains/data/stab_data_1e6_x2x6_factorial_small.RDS"))
```

```{r}
## find various combinations of diversity
var_expt <- readRDS(here("experiments/12_strains/data/ss_data_1e6_x2x6_factorial.RDS"))
stab_data <- readRDS(here("experiments/12_strains/data/stab_data_1e6_x2x6_factorial.RDS"))

@@

```{r eval = plot_ss_results}

@@

@@

p_overlay1 <- plot_ss_result2(var_expt[no_diversity,]$ss_res[[1]],
                             var_expt[max_diversty_all,]$ss_res[[1]],
                             xlims = c(-7, -1))
p_overlay1

p_overlay2 <- plot_ss_result2(var_expt[no_diversity,]$ss_res[[1]],
                             var_expt[max_only_CB_diversity,]$ss_res[[1]],
                             xlims = c(-7, -1))
p_overlay2

p_overlay3 <- plot_ss_result2(var_expt[no_diversity,]$ss_res[[1]],
                             var_expt[max_only_SBPB_diversity,]$ss_res[[1]],
                             xlims = c(-7, -1))
p_overlay3

@@

```{r eval = plot_ss_results}
tempp1 <- var_expt[no_diversity,]$ss_res[[1]] %>%
  filter(initial_N_CB == 1e10,
         log10(a_O) > -4.5, log10(a_O) < -4)
tempp2 <- var_expt[max_only_SBPB_diversity,]$ss_res[[1]] %>%
  filter(initial_N_CB == 1e10,
         log10(a_O) > -4.5, log10(a_O) < -4)

@@

```{r eval = plot_ss_results}
CB_vars <- unique(stab_data$CB_var_gmax_s)
SB_vars <- unique(stab_data$SB_var_gmax_s)

@@

### Raw
```{r eval = plot_ss_results}
all_stab_results %>%
  filter(Species == "O") %>%
  ggplot(aes(x = var_gmax, y = hyst_range_raw, col=var_treat, shape = as_factor(sim_length))) +
  geom_point() +
  xlab("Amount of trait variation\n[see text for units]") +
  ylab("Extent of bistability region\n[log10 oxygen diffusivity]") +
  labs(col = "Variation in\nonly these\nfunctional groups")
##ggsave("manuscript/figures/extent_of_bistab1.pdf", height = 4)

@@

```{r eval = plot_ss_results}
all_stab_results %>%
  filter(Species == "O") %>%
  ggplot(aes(x = var_gmax, y = hyst_range_log, col=var_treat, shape = as_factor(sim_length))) +
  geom_point() +
  xlab("Amount of trait variation\n[see text for units]") +
  ylab("Extent of bistability region\n[log10 oxygen diffusivity]") +
  labs(col = "Variation in\nonly these\nfunctional groups")
##ggsave("manuscript/figures/extent_of_bistab1.pdf", height = 4)

@@
